Bioverse: The Habitable Zone Inner Edge Discontinuity as an Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-09-13 src/tex/ms.tex
rephrase usage of data published in DL21

Nominally, the above models assume a \textit{dry melt} without dissolved volatiles.
Here, however, we consider a \textit{wet melt} magma ocean and take into account a radius decrease from retention of water in the melt~\citep{Dorn2021}.
The impact of the water distribution between melt and atmosphere on the change of the transit radius depends on the planet's mass and water content and is generally small compared to the radius inflation from the steam atmosphere.
%We follow \citet{Dorn2021} and use their computed radius deviations between a wet magma ocean and a solid mantle for a tropopause pressure~$P_\mathrm{iso}=\SI{0.1}{\bar}$.
We computed radius deviations between a wet magma ocean and a solid mantle following \citet{Dorn2021} and assuming a tropopause pressure~$P_\mathrm{iso}=\SI{0.1}{\bar}$.
We then added the (in almost all cases negative) radius deviations to the inflated planet radii computed for the dry melt case.

>>>>

Nominally, the above models assume a \textit{dry melt} without dissolved volatiles.
Here, however, we consider a \textit{wet melt} magma ocean and take into account a radius decrease from retention of water in the melt\reviii{ using the results published in \citet{Dorn2021}.}
The impact of the water distribution between melt and atmosphere on the change of the transit radius depends on the planet's mass and water content and is generally small compared to the radius inflation from the steam atmosphere.
%We follow \citet{Dorn2021} and use their computed radius deviations between a wet magma ocean and a solid mantle for a tropopause pressure~$P_\mathrm{iso}=\SI{0.1}{\bar}$.
We \reviii{obtained} radius deviations between a wet magma ocean and a solid mantle \reviii{using the numerical values from} \citet{Dorn2021} \reviii{that assume} a tropopause pressure~$P_\mathrm{iso}=\SI{0.1}{\bar}$.
We then added the (in almost all cases negative) radius deviations to the inflated planet radii computed for the dry melt case.
